Jane, John … Leslie? A Historical Method for Algorithmic Gender Prediction

### 2015-08-21 article.Rmd
NAPP in present tense

The next release of the Gender package will include a dataset from the [North Atlantic Population Project](https://www.nappdata.org/napp/). This dataset will include names from Canada, Great Britain, Germany, Iceland, Norway, and Sweden from 1801 to 1910.^[The North Atlantic Population Project, which is also project of the Minnesota Population Center, also includes data for the United States of America, but we have excluded it since IPUMS-USA and the SSA dataset is more suitable when focusing on that country alone.] The SSA, IPUMS, and NAPP datasets (and any future datasets to be added to the package) all have the same simple tabular format.^[The format of this data departs from the more generally desirable "tidy data" framework proposed by Hadley Wickham for performance reasons. By keeping the data in a "wider" format instead of a tidy format as defined by Wickham, the function is able to make its predictions faster [Wickham 2014b].] The columns contain the `name`, `year`, and number of `female` and `male` uses of that name in a particular year. This simple format makes it possible to extend the package to include any place and time period for which there is suitable data.^[We welcome such contributions at the [project's GitHub repository](https://github.com/ropensci/gender).]

>>>>

The gender package also features a dataset from the [North Atlantic Population Project](https://www.nappdata.org/napp/). This dataset includes names from Canada, Great Britain, Germany, Iceland, Norway, and Sweden from 1801 to 1910.^[The North Atlantic Population Project, which is also project of the Minnesota Population Center, also includes data for the United States of America, but we have excluded it since IPUMS-USA and the SSA dataset is more suitable when focusing on that country alone.] The SSA, IPUMS, and NAPP datasets (and any future datasets to be added to the package) all have the same simple tabular format.^[The format of this data departs from the more generally desirable "tidy data" framework proposed by Hadley Wickham for performance reasons. By keeping the data in a "wider" format instead of a tidy format as defined by Wickham, the function is able to make its predictions faster [Wickham 2014b].] The columns contain the `name`, `year`, and number of `female` and `male` uses of that name in a particular year. This simple format makes it possible to extend the package to include any place and time period for which there is suitable data.^[We welcome such contributions at the [project's GitHub repository](https://github.com/ropensci/gender).]
